---
title: 'MATH2270/MATH2237 Data Visualisation.'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Interactive Storytelling through dashboard.

• Tarun.S.Sarode (s3700754)

## Story URL

- Klasen, S., 2018. Human Development Indices And Indicators: A Critical Evaluation. [ebook] New York: UNDP Human Development Report Office. Available at: <http://hdr.undp.org/sites/default/files/klasen_final.pdf>.


## Data Source

- Hdr.undp.org. n.d. Human Development Data (1990-2018) | Human Development Reports. [online] Available at: <http://hdr.undp.org/en/data>. 

## Visualisation URL

- https://tarun-s-sarode.shinyapps.io/HDI-dashboard/


## Code 
```{r message=FALSE, warning=FALSE}
library(ggplot2)
library(mgcv)
library(readr)
library(shiny)
library(plotly)
library(rgeos)
library(maptools)
library(ggmap)
library(broom)
library(dplyr)
library(ggplot2)
library(maps)
library(mapdata)
library(gdata)
library(rgdal)
library(ggthemes)
library(scales)
library(ggrepel)
library(reshape)

# reading the data
hdiiii <- read.csv("hdi.csv")

# selecting only the columns required for the analysis.
hdiii<-hdiiii[,-c(1,4,6,8,10,12,14,16,18,20,22,24,26,28,30,32,34,36,38,40,42,44,46,48,50,52,54,56)]

# renaming the column names
colnames(hdiii)<-c('Country','1990','1991','1992','1993','1994',
                   '1995','1996','1997','1998','1999',
                   '2000','2001','2002','2003','2004',
                   '2005','2006','2007','2008','2009',
                   '2010','2011','2012','2013','2014',
                   '2015','2016','2017')

# using the melt function to make format the data for using the ggplot library.
mm<- melt.data.frame(hdiii,id='Country')
```


Inputs {.sidebar}
-----------------------------------------------------------------------

```{r}


 selectizeInput("xx", label= "Select Country Name(s) of Interest",
choices = unique(mm$Country), multiple = T, selected = mm$Country,
options = list(maxItems = 4))


```
__About HDI__

__What is Human Development Index?__


The Human Development Index (HDI) is a composite statistic (index) that measures key dimensions of human development, which are:
      
- Life Expectancy(a long and healthy life)
- Literacy Rate(being knowledgeable)
- Per Capital Income(a decent standard of living)

__Publication__

Since the drastically changed landscape of development,Select a country to see the Human development Index (HDI) of the Countries across years from 1990 to 2017.
     
 [See Paper Here](http://hdr.undp.org/sites/default/files/klasen_final.pdf)

__Data__

  [Download  HDI csv Data](http://hdr.undp.org/en/data)



Outputs
-----------------------------------------------------------------------
### Human Development Index 

```{r}

dataset1 <- reactive({ mm%>%filter(Country==input$xx)})

renderPlotly({
 ll<-ggplot(dataset1(),aes_string(x="variable" , y ='value' ,group='Country',color='Country' ))+
   geom_line()+ylim(min=0,max=1)+xlab('Years')+ylab('HDI Score')
   k<-ggplotly(ll)
   k
})

```

